Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52740 72bbbca6-d526-0410-a7d9-f06f51895060
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52741 72bbbca6-d526-0410-a7d9-f06f51895060
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52742 72bbbca6-d526-0410-a7d9-f06f51895060
+1
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52743 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table}[h]
\begin{tabular}{ll}
 \textbf{Code switching}: & You're a [Meirice\'{a}nach, c\'{e}n f\'{a}th] are you [foghlaim Gaeilge?!] \\
\textbf{Quotations}: & And then he said ` ' \\
 \textbf{Named entities}: & [Dr Jekyll] ha [Mr Hyde] embannet gant [\'{E}ditions Aber] \\
 \textbf{Interjections}: & Hey, that's great, [diolch yn fawr!] \\
 \textbf{Translations}: & Bloavezh mat d'an holl ! [Bonne ann\'{e} \`{a} tous !] \\
\end{tabular}
\caption{Some examples of text segments containing more than one language}
\label{table:examples}
\end{table}

@@

Code-switching and segment detection problems have been the subject of previous research. A good deal of work
has been done on detecting code-switched segments in speech data \cite{chan2004detection,lyu2006language}.
It is seen that language modelling techniques have shown promise earlier, such as in \cite{yu2013identification} 
the experiment on Mandarin-Taiwanese code-switched sentences show a high accuracy in terms of detecting code-switched sentences. \\

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{ll}
 \textbf{Code switching}: & You're a [Meirice\'{a}nach, c\'{e}n f\'{a}th] are you [foghlaim Gaeilge?!] \\
\textbf{Quotations}: & The anthem starts with the words [`Mae hen wlad fy nhadau\ldots'] \\
 \textbf{Named entities}: & [Dr Jekyll] ha [Mr Hyde] embannet gant [\'{E}ditions Aber] \\
 \textbf{Interjections}: & Hey, that's great, [diolch yn fawr!] \\
 \textbf{Translations}: & Bloavezh mat d'an holl ! [Bonne ann\'{e} \`{a} tous !] \\
\end{tabular}
\caption{Some examples of text segments containing more than one language}
\label{table:examples}
\end{center}
\end{table}

@@

Code-switching and segment detection problems have been the subject of previous research. A good deal of work
has been done on detecting code-switched segments in speech data \cite{chan2004detection,lyu2006language}.
It is seen that language modelling techniques have shown promise earlier, such as in \newcite{yu2013identification} 
the experiment on Mandarin-Taiwanese code-switched sentences show a high accuracy in terms of detecting code-switched sentences. \\
